Processing simulation output

### 2020-05-14 results/README.Rmd
add r scripts results readme

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(tidyverse)
library(knitr)
library(flextable)
library(officer)
```

@@

Create table for manuscript (all means over 15 runs)
```{r, results = "asis"}
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rjson)
library(tidyverse)
library(knitr)
library(flextable)
library(officer)
```

@@

Create table for manuscript (all means over 15 runs)
```{r, echo = FALSE, results = "asis"}
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))
